### 2009-02-19 docs/paper.tex
--

Дифференциальная задача:
\begin{equation*}
\Delta u(\phi, \lambda) = f(\phi, \lambda)
u\|_{\partial\Omega} = u_0
\end{equation*}

Численная задача:
\begin{equation*}
\begin{split}
(\frac{1}{cos\psi}\frac{\partial}{\partial \phi} \phi_i, cos\phi \frac{\partial}{\partial \phi} \phi_j) = -(f, \phi_j), \forall j, \forall i, \text{ для внутренних узлов } \\
u = u_0 \phi_i, \text { для граничных узлов, }
\end{split}
\end{equation*}
где $\phi_i$, $\phi_j$ - базисные функции.

@@

Система уравнений:
\begin{equation*}
\sum_j x_j \sum_{k: \{j\in\bigtriangleup_k, i\in\bigtriangleup_k\}}\int_{\bigtriangleup_k}\frac{1}{cos\psi}(\frac{\partial}{\partial \phi} \phi_i) cos\phi (\frac{\partial}{\partial \phi} \phi_j) ds = \sum_{k:\{i\in\bigtriangleup_k\}}\int_{\bigtriangleup_k}f \phi_j ds,
\end{equation*}
где
\begin{equation*}
u(\phi,\lambda)=\sum_i x_i \phi_i(\phi, \lambda),\\
f(\phi,\lambda)=\sum_i f_i \phi_i(\phi, \lambda).
\end{equation*}

>>>>

Дифференциальная задача:
\begin{equation*}
\begin{split}
\Delta u(\phi, \lambda) = f(\phi, \lambda)\\
u|_{\partial\Omega} = u_0
\end{split}
\end{equation*}

Численная задача:
\begin{equation*}
\begin{split}
(\frac{1}{cos\psi}\frac{\partial}{\partial \phi} \phi_i, cos\phi \frac{\partial}{\partial \phi} \phi_j)
+(\frac{1}{cos\psi}\frac{\partial}{\partial \lambda}\phi_i, \frac{1}{cos\psi}\frac{\partial}{\partial \lambda}\phi_j ) = -(f, \phi_j), \forall j, \forall i, \text{ для внутренних узлов } \\
u = u_0 \phi_i, \text { для граничных узлов, }
\end{split}
\end{equation*}
где $\phi_i$, $\phi_j$ - базисные функции.

@@

Система уравнений:
\begin{equation*}
\sum_j x_j \sum_{k: \{j\in\bigtriangleup_k, i\in\bigtriangleup_k\}}\int_{\bigtriangleup_k}\frac{1}{cos\psi}(\frac{\partial}{\partial \phi} \phi_i) cos\phi (\frac{\partial}{\partial \phi} \phi_j)+\frac{1}{cos^2\psi}\phi_i\phi_j ds = \sum_{k:\{i\in\bigtriangleup_k\}}\int_{\bigtriangleup_k}f \phi_j ds,
\end{equation*}
где
\begin{equation*}
u(\phi,\lambda)=\sum_i x_i \phi_i(\phi, \lambda),\\
f(\phi,\lambda)=\sum_i f_i \phi_i(\phi, \lambda).
\end{equation*}
